\documentclass[12pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[margin=12mm]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{fontawesome}
\usepackage{tabularx}
\usepackage{enumitem}

% remove all headings and footers completely
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Table formatting
\setlength{\parindent}{0mm}
\setlength{\tabcolsep}{0mm}

% Format for all section headings
\usepackage{titlesec}
\titleformat{\section}[display]
{\vspace{-5mm}\large\scshape}
{}{0mm}{}
[\titlerule]

% Custom page header command
\newcommand{\header} [4] {
	\begin{tabularx} {\textwidth} { 
	  	>{\raggedright\arraybackslash}X
	  	>{\raggedleft\arraybackslash}X }
	
		\textbf{\LARGE{#1}}  & #2  \\[1mm]
		#3  & #4
	\end{tabularx}
}


% Custom commands for displaying unordered lists
\newcommand{\subHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\subHeadingListEnd}{\end{itemize}}

\newcommand{\subHeading} [4] {
	\item 
	\begin{tabularx}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{\small#3} & \textit{\small #4}
	\end{tabularx}
	\vspace{-2mm}
}

\newcommand{\subItem} [2] {
	\raggedright
	\item[$\circ$] \small {
		\textbf{#1}{: #2}
	}
}

% ---------------------------------- BEGIN DOCUMENT ----------------------------
\begin{document}

% Heading
\header
{Alberto Mosconi} % top-left
{\href{https://github.com/albertomosconi}{github.com/albertomosconi \faGithub}} % top-right
{\href{mailto:albertomaria.mosconi@gmail.com}{albertomaria.mosconi@gmail.com}} % bottom-left
{\href{https://albertomosconi.it}{albertomosconi.it \faGlobe}} %bottom-right

% Work Experience
\section{\faLaptop \hspace{0mm} Work Experience}

\subHeadingListStart
\subHeading
{CBIM}{Pavia, IT}
{Web Developer}{Oct 2019 -- Apr 2020}
\begin{itemize}
  \subItem {Full Stack Development}
  {Built two professional web applications using ReactJS with Bootstrap. Integrated them with two databases through rest APIs with SpringBoot.}

\end{itemize}
\subHeadingListEnd

% Projects
\section{\faWrench \hspace{0mm} Projects}

\subHeadingListStart
\subItem {\href{https://slashbinteam.github.io}{./bin}}
{A mobile application with a modern UI to help with recycling. It uses a machine learning model, trained on a dataset of images, to predict how the photographed item should be recycled. In addition the user can choose to send the photo to the database and further improve the accuracy of the predictions.}

\subItem {\href{www.albertomosconi.it}{albertomosconi.it}}
{Built my website using ReactJS and Bootstrap as a front-end and Firebase Functions to handle back-end calls. It also utilizes the Github API to display all my projects.}

\subHeadingListEnd

% Education
\section{\faBook \hspace{0mm} Education}

\subHeadingListStart
\subHeading
{Polytechnic University of Milan}{Milan, IT}
{Bachelor of Engineering of Computing Systems.}{Sept. 2018 -- Today}

\subHeading
{Liceo Scientifico T. Taramelli}{Pavia, IT}
{Scientific High School Diploma.}{Sept. 2013 -- July. 2018}

\subHeading
{Coursera, Udemy, Udacity, EdX}{Online}
{Completed several courses on Web Development and Machine Learning.}{2015 -- Today}
\subHeadingListEnd

% Skillset
\section{\faLightbulbO \hspace{0mm} Skillset}

\raggedright
\textbf{Web Development:}
{ReactJS,  GatsbyJS, WordPress, Firebase, Bootstrap, HTML, CSS, Javascript, Python.} \\[3mm]

\textbf{Machine Learning:}
{PyTorch, Numpy, MatPlotLib, Python.}

\end{document}